
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-6pt}
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape S M A Nahian} \\ \vspace{1pt}
    500 Memorial Drive, Cambridge, MA 02139, USA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 (857) 331-8436 ~ \href{mailto:nahian@mit.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{nahian@mit.edu}} ~ 
    \href{https://www.linkedin.com/in/SMANahian/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/SMANahian}}  ~
    \href{https://github.com/SMANahian}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/SMANahian}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Massachusetts Institute of Technology}{August 2025 -- May 2029}
            {Bachelor of Science — Undeclared}{Massachusetts, USA}

            	\textit{Activities: HackMIT; Member of the MIT A team in Collegiate Chess League (Fall 2025)}

        % \vspace{3mm}    
            	\textit{Relevant Courses:} Distributed Computer Systems Engineering (6.5840), Randomized Algorithms (6.5220), Computation Structures (6.1910), Fundamentals of Programming (6.1010), Intro to CS Programming in Python (6.100A), Intro Program in C \& Assembly (6.1903)
    
        \resumeSubheading
            {Dhaka College}{February 2023 -- October 2024}
            {Higher Secondary Certificate, Science (Grade: 5.00/5.00)}{Dhaka, Bangladesh}

        \resumeSubheading
            {Shamsul Hoque Khan School and College}{January 2017 -- November 2022}
            {Secondary School Certificate, Science (Grade: 5.00/5.00)}{Dhaka, Bangladesh}

        \resumeSubheading
            {SDS Academy}{January 2011 -- December 2016}
            {Primary Education Completion (Grade: 5.0/5.0)}{Shariatpur, Bangladesh}
        
    \resumeSubHeadingListEnd
%-----------INVOLVEMENT---------------
\section{Honors \& Awards}
\begin{itemize}[leftmargin=0in, label={}]
    \small
    \item {\textbf{Iranian Geometry Olympiad (IGO)}: Silver Medal (Free Level, 2024, Country Rank \#1); Bronze (Advanced, 2023, Country \#1, World \#52); Bronze (Advanced, 2022, Country \#1, World \#21); Silver (Intermediate, 2021, Country \#2, World \#29); Silver (Intermediate, 2020, Country \#1, World \#20).}
    \item {\textbf{International Mathematical Olympiad (IMO)}: Bronze Medals (2024 Country \#2 World \#252; 2023 Country \#1 World \#145); Honorable Mention (2022). Represented Bangladesh 3 consecutive years.}
    \item {\textbf{Asia Pacific Mathematical Olympiad (APMO)}: Silver Medals (2022, 2023); Bronze Medal (2024); represented Bangladesh 3 consecutive years.}
    \item {\textbf{Iranian Combinatorics Olympiad (ICO)}: Bronze Medal (Advanced Category, 2021, Country Rank \#1, World \#30).}
    \item {\textbf{Bangladesh Junior Science Olympiad (BdJSO)}: 1st Place National Round (2021).}
    \item {\textbf{Science Olympiad (National Science \& Technology Week)}: 1st Prize (2020); District Champion (2019, 2020).}
    \item {\textbf{Asia Pacific Informatics Olympiad (APIO)}: National Finalist (2024) — Ranked 5th in Bangladesh, 210th worldwide.}
    \item {\textbf{ICPC Asia Dhaka Regional} (2023): 6th Place overall as guest high school team (Team IOI1).}
    \item {\textbf{Bangladesh Olympiad in Informatics (BdOI)}: Bronze Medals (2023 Ranked 4th nationally; 2024 Ranked 5th nationally).}
    \item {\textbf{Father Timm Memorial Programming Contest (FTMPC)}: Bronze Medals (2023, 2024).}
    \item {\textbf{USACO} Gold Division (Promoted January 2023).}
    \item {\textbf{Champion of the Champions (BdMO)}: 2021–2024; \textbf{National Winner} (2016, 2017, 2019).}
    \item {\textbf{STAR Scholar} – Search for Talented Ramanujans (2023) with $\$500$ prize for excellence in problem solving.}
    \item {\textbf{William Lowell Putnam Mathematical Competition}: Ranked 231 (Top 5\%) in the 86th Putnam (2025).}
    \item {\textbf{Arena FIDE Master (AFM)} title awarded October 2024 by FIDE.}
    \item {\textbf{Master Rank at Codeforces}: Achieved Aug 2024 (Max Rating 2100+), top ~1\%.}
    \item {\textbf{Merit-Based Govt. Scholarship} – SSC 2022 (Nov 2022) and PEC 2016 (Feb 2017), Talentpool category.}
    \item {\textbf{3rd Place} – Astrophysics Contest (Gonitzoggo, Oct 2020).}
\end{itemize}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Programming/Scripting Languages}{: Python, C++, C, Rust, JavaScript, PHP, Java} \\
        \textbf{Technologies/Frameworks}{: Linux, GitHub, Flask, Verus, MongoDB} \\
        % \textbf{Technical Skills}{: Web Development, Graph Theory, Algorithmic Problem, Research} \\
        % \textbf{Soft Skills}{: Problem-Solving, Teaching, Teamwork} \\
    }}
\end{itemize}



%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
                    	\textbf{Bengali}{: Native or bilingual proficiency} \\
                    	\textbf{English}{: Professional working proficiency} \\
                    	\textbf{Hindi}{: Elementary proficiency} \\
    }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Cybersecurity at MIT Sloan (CAMS)}{September 2025 -- Present}
            {Undergraduate Research Assistant}{Massachusetts, USA}
            \resumeItemListStart
                \resumeItem{Developing graph-based models to analyze and minimize risk propagation in AI supply chains.}
                \resumeItem{Designing optimization methods to identify the most critical components to harden, sign, or verify for maximum security impact.}
            \resumeItemListEnd
            
        \resumeSubheading
            {Beneficial AI Foundation}{September 2025 -- Present}
            {Undergraduate Research Assistant}{Massachusetts, USA}
            \resumeItemListStart
                \resumeItem{Developing AI tools to accelerate and automate formal verification workflows.}
                \resumeItem{Contributing to Dalek-Lite, a Rust-based fork of dalek-cryptography/curve25519-dalek, aimed at the formal verification of elliptic-curve cryptography using Verus. GitHub: \texttt{\href{https://github.com/Beneficial-AI-Foundation/dalek-lite}{Beneficial-AI-Foundation/dalek-lite}}}
            \resumeItemListEnd
        
        \resumeSubheading
            {Mercor}{July 2025 -- August 2025}
            {Mathematics Expert (Olympiad) — Contract}{Remote}
        
        \resumeSubheading
            {UC Irvine}{October 2023 -- August 2025}
            {Research Collaborator — Graph Theory (Internship)}{Irvine, California, USA \textit{(Remote)}}
            \resumeItemListStart
                \resumeItem{Conducted research under Prof. Wayne Hayes focused on graph theory and network analysis.}
                \resumeItem{Contributed to a tool used in biological and computational network research.}
                \resumeItem{Worked on algorithm design and performance optimization.}
            \resumeItemListEnd
            
        \resumeSubheading
            {Gonitzoggo}{August 2023 -- July 2025}
            {Internship}{Bangladesh, Remote}
            \resumeSubSubheading{Engineering Team Member}{September 2024 -- July 2025}
                \resumeItemListStart
                    \resumeItem{Built key features and redesigned contest UI and logic for version 3, improving usability.}
                \resumeItemListEnd
            \resumeSubSubheading{Developer}{August 2023 -- September 2024}
                \resumeItemListStart
                    \resumeItem{Identified a major security flaw and was recruited as a developer after reporting it.}
                    \resumeItem{Built key features, including author credit system for contests and profile picture cropping.}
                    \resumeItem{Simplified contest page UI and button logic for improved usability.}
                \resumeItemListEnd
  \resumeSubHeadingListEnd



% ------------Research--------------
\section{Research}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{BLANT Project (Under Prof. Wayne Hayes, UCI)}}{October 2023 -- August 2025}
            \resumeItemListStart
                % \resumeItem{Invented a new structure for the pre-computed table, allowing BLANT to work up to graphlets of size k=10. Developed a novel method to allow BLANT to estimate the actual counts rather than only the graphlet's concentrations (ratio of the count). Improved the sampling methods of BLANT. Currently working on publishing a confidential sub-project of BLANT. Details at : \texttt{\href{https://github.com/waynebhayes/BLANT}{https://github.com/waynebhayes/BLANT}}}
                \resumeItem{Developed a method to estimate absolute graphlet counts from relative concentrations using star-motifs}
                \resumeItem{Derived normalization formulas for two existing sampling methods: NBE (Node-Based Expansion) and EBE (Edge-Based Expansion), making them usable in practice with reduced statistical noise}
                \resumeItem{Improved the $\alpha$-computation algorithm in MCMC sampling, reducing runtime from hours to seconds for k=8}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


% -----------Publications--------------
\section{Publications}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{The Unseen Connections: Link Prediction via Pattern Matching in Large Networks} $|$ \emph{Cell Press Patterns} (under review)}{October 9, 2025}
            \resumeItemListStart
                \resumeItem{Worked with Prof. Wayne Hayes to develop BLANT-Predict, a topology-based link prediction model using higher-order graphlet structures that outperforms 13 state-of-the-art methods on large real-world networks.}
                \resumeItem{Introduced a novel ``time-travel'' evaluation framework for realistic forecasting.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{dalek-lite} $|$ \emph{Rust, Verus}}{September 2025 -- January 2026}
            \resumeItemListStart
                \resumeItem{Contributing to a formally verifiable Rust fork of curve25519-dalek by specifying and verifying scalar/field operations, enforcing limb-boundedness and modular invariants, and ensuring constant-time behavior for end-to-end ECC verification. GitHub: \texttt{\href{https://github.com/Beneficial-AI-Foundation/dalek-lite}{Beneficial-AI-Foundation/dalek-lite}}}
            \resumeItemListEnd
        
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{BeatVote} $|$ \emph{Python, Flask, MongoDB, Chrome/Brave Ext}}{September 2025}
            \resumeItemListStart
                \resumeItem{Built a collaborative karaoke/party music room platform at HackMIT 2025 with secure login/guest access and real-time queue updates to keep every room in sync. GitHub: \texttt{\href{https://github.com/SMANahian/BeatVote}{SMANahian/BeatVote}}}
                \resumeItem{Implemented a YouTube Data API proxy and a companion browser extension that pins the host room, drives playback in dedicated tabs, and adds an in-page player toggle.}
            \resumeItemListEnd

        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{BLANT: Basic Local Alignment of Network Topology} $|$ \emph{C, C++, Python}}{October 2023 -- August 2025}
            \resumeItemListStart
                \resumeItem{Improved graphlet-sampling methods and performance under Prof. Wayne Hayes; details in Research. GitHub: \texttt{\href{https://github.com/waynebhayes/BLANT}{waynebhayes/BLANT}}}
            \resumeItemListEnd

        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{Chess Analyzer} $|$ \emph{Python, Chess}}{June 2025}
            \resumeItemListStart
                \resumeItem{Analyzes a player's PGN game history to detect recurring opening mistakes and automatically generates replayable practice positions for those errors. GitHub: \texttt{\href{https://github.com/SMANahian/chess-analyzer}{SMANahian/chess-analyzer}}}
            \resumeItemListEnd
        
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{ssehC} $|$ \emph{C, Chess}}{September 2024 -- April 2025}
            \resumeItemListStart
                \resumeItem{Built a chess engine from scratch in C with move generation, evaluation, and minimax with alpha-beta; deployed as a Lichess bot that achieved a 2000+ rating. GitHub: \texttt{\href{https://github.com/SMANahian/ssehC}{SMANahian/ssehC}}}
            \resumeItemListEnd
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{Spotify Addon (Synced Lyrics for Spotify)} $|$ \emph{Java}}{February 2024}
            \resumeItemListStart
                \resumeItem{Expanded a Java-based lyrics widget by integrating the lrclib.net synced-lyrics API, formatting output for the app's UI/timing engine, and contributing changes upstream. GitHub: \texttt{\href{https://github.com/LabyStudio/spotify-addon}{LabyStudio/spotify-addon}}}
            \resumeItemListEnd

        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{CP Calendar} $|$ \emph{Python, Flask}}{February 2022}
            \resumeItemListStart
                \resumeItem{Customizable calendar that aggregates 120+ competitive programming contest feeds via Clist API; supports keyword/platform filters and personal .ics generation for Google Calendar sync. Live: \texttt{\href{https://cpcalendar.pythonanywhere.com/}{cpcalendar.pythonanywhere.com}} \; GitHub: \texttt{\href{https://github.com/SMANahian/cp-calendar}{SMANahian/cp-calendar}}}
            \resumeItemListEnd

        % \vspace{-3mm}
    \resumeSubHeadingListEnd


% -----------Activities
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Bangladesh Mathematical Olympiad (BdMO)}{February 2022 -- November 2025}
            {Academic Team Member \& Mentor}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Volunteer mentor for national and junior math Olympiad camps.}
                \resumeItem{Conducted advanced classes and discussion sessions; mentored students in algebra, geometry, and combinatorics.}
                \resumeItem{Prepared problem sets and handwritten lecture notes; coached students who qualified for national teams and higher rounds.}
            \resumeItemListEnd

        \resumeSubheading
            {Gonitkonya — Bangladesh Girls' Mathematics Foundation}{March 2022 -- May 2025}
            {Academic Team Member}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Taught and mentored female Olympiad participants in national and EGMO-focused camps.}
                \resumeItem{Trained Bangladesh's EGMO teams in 2022, 2023, and 2024; conducted live sessions and mock tests.}
                \resumeItem{Authored 10+ original problems; worked to increase female representation in high-level math competitions.}
            \resumeItemListEnd

        \resumeSubheading
            {Thonk \& Code}{September 2024 -- March 2025}
            {Co-Founder \& Mentor}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Launched an initiative to support beginner and intermediate students in the Bangladesh Olympiad in Informatics (BdOI).}
                \resumeItem{Created structured curriculum and content; promoted a mentorship culture within the BdOI community.}
            \resumeItemListEnd

        \resumeSubheading
            {NEMOP}{August 2024 -- August 2025}
            {Founder}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Year-long online mathematics training program inspired by India's OMC to prepare Bangladeshi students for IMO.}
                \resumeItem{Designed weekly problem sets and biweekly exams; taught advanced topics and Olympiad strategies.}
            \resumeItemListEnd

        \resumeSubheading
            {Somantoral Magazine}{September 2023 -- December 2024}
            {Web Developer \& Content Writer}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Contributed articles and web features to a student-run math magazine focused on accessible advanced topics.}
            \resumeItemListEnd

        \resumeSubheading
            {Gonitzoggo}{May 2022 -- August 2024}
            {Academic Team Member \& Tutor}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Created Olympiad-level problems and taught in online courses and practice programs for national Olympiad students.}
            \resumeItemListEnd

        \resumeSubheading
            {Shamsul Hoque Khan School \& College Scout Group}{January 2017 -- January 2018}
            {Scout}{Dhaka, Bangladesh}
            \resumeItemListStart
                \resumeItem{Participated in school scout camps and community volunteering; developed teamwork and leadership skills.}
            \resumeItemListEnd    
    \resumeSubHeadingListEnd    



\end{document}
