
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-6pt}
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape S M A Nahian} \\ \vspace{1pt}
    500 Memorial Drive, Cambridge, MA 02139, USA \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 (857) 331-8436 ~ \href{mailto:nahian@mit.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{nahian@mit.edu}} ~ 
    \href{https://www.linkedin.com/in/SMANahian/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/SMANahian}}  ~
    \href{https://github.com/SMANahian}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/SMANahian}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Massachusetts Institute of Technology}{August 2025 -- Present}
            {Bachelor of Science}{Massachusetts, USA}

    % \vspace{3mm}    
    \textit{Relevant Courses:} Distributed Computer Systems Engineering, Randomized Algorithms, Computation Structures, Fundamentals of Programming, Intro to Programming in C \& Assembly
  
    \resumeSubHeadingListEnd
%-----------INVOLVEMENT---------------
\section{Achievements}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Mathematical Olympiads}{: William Lowell Putnam Mathematical Competition Top 250 (2025); International Mathematical Olympiad Bronze Medal (2023, 2024) and Honorable Mention (2022); Asia Pacific Mathematics Olympiad Silver Medal (2022, 2023) and Bronze Medal (2024)
        } \\
        \vspace{2mm}
        \textbf{Competitive Programming}{: Asia Pacific Informatics Olympiad Finalist (2024); ICPC Asia Dhaka Regional 6th Position as a guest high school team (2023); Bangladesh Olympiad in Informatics Bronze Medal (2023, 2024); Master rank at CodeForces} \\
        \vspace{2mm}
        \textbf{Chess}{: Arena FIDE Master (AFM) at International Chess Federation---FIDE}
    }}
\end{itemize}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
        \textbf{Programming/Scripting Languages}{: Python, C++, C, Rust, JavaScript, PHP, Java} \\
        \textbf{Technologies/Frameworks}{: Linux, GitHub, Flask, Verus, MongoDB} \\
    }}
\end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Cybersecurity at MIT Sloan (CAMS)}{September 2025 -- Present}
            {Undergraduate Research Assistant}{Massachusetts, USA}
            \resumeItemListStart
                \resumeItem{Developing graph-based models to analyze and minimize risk propagation in AI supply chains.}
                \resumeItem{Designing optimization methods to identify the most critical components to harden, sign, or verify for maximum security impact.}
            \resumeItemListEnd
            
        \resumeSubheading
            {Beneficial AI Foundation}{September 2025 -- Present}
            {Undergraduate Research Assistant}{Massachusetts, USA}
            \resumeItemListStart
                \resumeItem{Developing AI tools to accelerate and automate formal verification workflows.}
                \resumeItem{Contributing to Dalek-Lite, a Rust-based fork of dalek-cryptography/curve25519-dalek, aimed at the formal verification of elliptic-curve cryptography using Verus. GitHub: \texttt{\href{https://github.com/Beneficial-AI-Foundation/dalek-lite}{Beneficial-AI-Foundation/dalek-lite}}}
            \resumeItemListEnd
            
        \resumeSubheading
            {UC Irvine}{October 2023 -- August 2025}
            {Research Collaborator --- Graph Theory (Internship)}{Irvine, California, USA \textit{(Remote)}}
            \resumeItemListStart
                \resumeItem{Conducted research under Prof. Wayne Hayes on graph theory, network analysis, and algorithm design.}
                \resumeItem{Contributed to BLANT, a tool for computational network research; improved sampling and performance.}
            \resumeItemListEnd

        \resumeSubheading
            {Gonitzoggo}{August 2023 -- July 2025}
            {Engineering Team Member}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Identified a major security flaw and was recruited as a developer after reporting it.}
                \resumeItem{Built key features and redesigned contest UI and logic for version 3, improving usability.}
            \resumeItemListEnd
  \resumeSubHeadingListEnd



% ------------Research Publications--------------
\section{Research Publications}
\begin{itemize}[leftmargin=0.15in, label={$\vcenter{\hbox{\tiny$\bullet$}}$}]
    \small
    \item \textbf{S M A Nahian}, Joel Rarang, Wayne B. Hayes. ``Sampling Methods for Graphlet Estimation.'' \textit{PLOS ONE} (Under Review).
    \item Wayne B. Hayes, Kimia Yazdani, \textbf{S M A Nahian}, Ezra Alemu. ``The Unseen Connections: Link Prediction via Pattern Matching in Large Networks.'' \textit{Cell Press Patterns} (Under Review). \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5579862}{[SSRN]}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{BeatVote} $|$ \emph{Python, Flask, MongoDB, Chrome Extension}}{September 2025}
            \resumeItemListStart
                \resumeItem{Built a collaborative karaoke and party music room platform at HackMIT 2025 in a team of four.}
                \resumeItem{Engineered a Flask + MongoDB stack with secure login, guest access, and real-time queue updates.}
            \resumeItemListEnd
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{Chess Analyzer} $|$ \emph{Python, Chess}}{June 2025}
            \resumeItemListStart
                \resumeItem{Built a tool that analyzes a player's games to detect recurring opening mistakes and generates targeted training positions for practice.}
            \resumeItemListEnd
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{ssehC --- Chess Engine} $|$ \emph{C}}{September 2024}
            \resumeItemListStart
                \resumeItem{Created a chess engine from scratch implementing minimax search with alpha-beta pruning; deployed as a Lichess bot achieving 2000+ rating.}
            \resumeItemListEnd
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{Spotify Addon --- Synced Lyrics} $|$ \emph{Java}}{February 2024}
            \resumeItemListStart
                \resumeItem{Extended an open-source Spotify lyrics widget with multilingual support via lrclib.net API; PR merged by original author.}
            \resumeItemListEnd
        \vspace{-4mm}
        \resumeProjectHeading
            {\textbf{CP Calendar} $|$ \emph{Python, Flask}}{February 2022}
            \resumeItemListStart
                \resumeItem{Created a customizable online calendar that aggregates competitive programming contests from 120+ online judges, with filtering and .ics sync.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


% -----------Extracurricular Activities (Academic/Olympiad)-----------
\section{Teaching \& Mentorship}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Problem Setter, Academic Team Member \& Mentor}{February 2022 -- November 2025}
            {Bangladesh Mathematical Olympiad (BdMO)}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Volunteer mentor for national and junior math Olympiad camps; conducted advanced math classes and discussion sessions.}
            \resumeItemListEnd

        \resumeSubheading
            {Problem Setter, Academic Team Member \& Mentor}{March 2022 -- May 2025}
            {Gonitkonya --- Bangladesh Girls' Mathematics Foundation}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Taught and mentored female Olympiad participants in national and EGMO-focused camps; trained the Bangladesh team for EGMO in 2022, 2023, and 2024.}
            \resumeItemListEnd

        \resumeSubheading
            {Founder}{August 2024 -- August 2025}
            {NEMOP --- Year Long Online Mathematics Training Program}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Founded NEMOP, inspired by India's OMC, to train top Bangladeshi students for the International Mathematical Olympiad (IMO).}
            \resumeItemListEnd

        \resumeSubheading
            {Co-Founder \& Mentor}{September 2024 -- March 2025}
            {Thonk \& Code}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Launched Thonk \& Code to support beginner and intermediate students in the Bangladesh Olympiad in Informatics (BdOI).}
            \resumeItemListEnd

        \resumeSubheading
            {Academic Team Member \& Tutor}{May 2022 -- August 2024}
            {Gonitzoggo}{Bangladesh}
            \resumeItemListStart
                \resumeItem{Created Olympiad-level math problems and taught in Gonitzoggo's online courses and practice programs for national Olympiad students.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd



\end{document}
